{\TheTitle}\thanks{Submitted to the editors DATE. \funding{This work was funded by the Fog Research Institute under contract no.~FRI-454.}}

### 2017-10-12 ssc-0-0.tex
writing

The semi-implicit formula is a rule for integrating systems of
ordinary differential equations \cite{jkp-132-312,jkp-93-144}.  It
is often used as a method of lines, to solve stochastic partial
differential equations that occur when phase space Monte-Carlo
methods are used in quantum optics and in atom optics \cite{pra-58-4824}.
This is done as a method of lines, in which the spatial axes are
discretised, often by spectral derivatives, to give a system of
ordinary differential equations \cite{2000-Trefethen-Spectral}.
The semi-implicit formula is then used to integrate these.

{\bf Relate Hilbert space expansions to methods of lines.}

>>>>

% formula equations
The semi-implicit formula is a rule for integrating systems of
ordinary differential equations \cite{jkp-132-312,jkp-93-144}.  It
is often used as a method of lines, to solve stochastic partial
differential equations that occur when phase space Monte-Carlo
methods are used in quantum optics and in atom optics \cite{pra-58-4824}.
These equations are related to Schr\"odinger's equation,
\begin{equation}
    \frac{\partial\psi}{\partial t} = -\del^2\psi + V\psi,
\end{equation}
with additional nonlinear and random terms.  The spatial axes are
discretised, often using spectral derivative operators, to give a
system of ordinary or stochastic differential equations
\cite{2000-Trefethen-Spectral}, and the semi-implicit formula is
used to integrate these equations.

{\bf Relate Hilbert space expansions to methods of lines using sync wave packets.}
